---
output:
  github_document:
    html_preview: false
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "images/README-"
)
```


## Overview

`"dieroller"` is a minimal [R](http://www.r-project.org/) package that provides functions to simulate rolling a die.

* `die()` creates a die object (of class `"die"`)
* `roll()` tosses a die object, producing a `"roll"` object.
* `plot()` method for a `"roll"` object to plot frequencies of die rolls.
* `summary()` method for a `"roll"` object.


## Motivation

This package has been developed to illustrate some of the concepts behind the creation of an R package.


## Installation

Install the development version from GitHub via the package `"devtools"`:

```r
# development version from GitHub:
#install.packages("devtools") 

# install "dieroller" (without vignettes)
devtools::install_github("jonathansun5/dieroller")

# install "dieroller" (with vignettes)
devtools::install_github("jonathansun5/dieroller", build_vignettes = TRUE)
```


## Usage

```{r example}
library(dieroller)

# default die
die1 <- die()
die1

# 1 roll of die1
roll(die1)

# 10 rolls of die1
roll10 <- roll(die1, times = 10)
roll10

# summary
summary(roll10)



# 100 rolls
roll100 <- roll(die1, times = 100)

# summary
summary(roll100)

# custom weighted die
str_die <- die(
  sides = c('a', 'b', 'c', 'd', 'e', 'f'),
  prob = c(0.075, 0.1, 0.125, 0.15, 0.20, 0.35))

# roll 20 times on a pseudo-fair die (remove `set.seed(123)` for different outputs)
set.seed(123)
str_rolls <- roll(str_die, times = 20)
str_rolls

# summary of custom weighted die
summary(str_rolls)



# 50 rolls of a pseudo-fair die (remove `set.seed(123)` for different outputs)
fair_die <- die()
set.seed(123)
fair_50rolls <- roll(fair_die, times = 50)

#summary of 50 fair rolls
fair50_sum <- summary(fair_50rolls)
fair50_sum

# plot method
plot(fair_50rolls)



# roll pseudo-fair die 500 times (remove `set.seed(123)` for different outputs)
set.seed(123)
fair_die <- die()
fair500 <- roll(fair_die, times = 500)

# summary method
summary(fair500)

# extracting roll in position 500
fair500[500]

# replacing last roll with "1"
fair500[500] <- 1
fair500[500]

# new summary with the modified roll
summary(fair500)

# plot method
plot(fair500)

# adding 100 rolls
fair600 <- fair500 + 100

# new summary with the modified roll plus 100 more rolls
summary(fair600)

# plot method
plot(fair600)
```
